Dynamical modeling of tidal streams

### 2013-12-31 tex/ms.tex
streams: bib tweak
streams: add figure of density distribution and description

Tidal streams hold enormous promise as probes of both the large-scale
structure of the Milky Way (MW) halo's density distribution
\citep[\eg,][]{Johnston99a,Koposov10a} and its small-scale
fluctuations \citep{Carlberg09a,Carlberg12a}. However, two factors
have hampered the practical use of tidal streams in obtaining
constraints on the MW gravitational potential. First, streams do not
trace a single orbit, which has led to confusion over how to best fit
streams and over how problematic the single-orbit approximation really
is \citep{Eyre11a,Sanders13a}. Second, approaches that go beyond the
single-orbit assumption encounter practical difficulties of
computational cost and observational data quality making many of these
approaches impractical for real, noisy data
\citep{Sanders13b,PriceWhelan13a}. Observed gaps in tidal streams may
be due to interactions with dark--matter subhalos \citep{Yoon11a}, but
spurious underdensities could be created by the dynamics of stream
stars. This hinders our ability to use underdensities in star counts
along a tidal stream in order to constrain the number of encounters
with dark satellites and their masses \citep{Ngan14a}. Fast,
generative models of tidal streams would greatly benefit both of these
applications.

@@

@@

Similar procedures can be followed to evaluate other projections and
marginalizations of the PDF, \eg, $p(b|l)$ for the observed track of
the stream on the sky, to convolve the PDF with observational
uncertainties, and to calculate moments of the PDF, \eg, the density
and velocity dispersion along the stream.

@@

\bibitem[{{Binney} \& {Tremaine}(2008)}]{binneytremaine}
  Binney,~J. \& Tremaine,~S. 2008, Galactic Dynamics: Second Edition
\bibitem[Binney(2008)]{Binney08a}
  Binney,~J. 2008, \mnras, 386, L47
\bibitem[Binney(2012)]{Binney12a}
  Binney,~J. 2012, \mnras, 426, 1324
\bibitem[Bovy \etal(2011)]{Bovy11a}
  Bovy,~J., Hogg,~D.~W., \& Roweis,~S.~T. 2011, Ann. Appl. Stat. 5, 1657, arXiv:0905.2979v1
\bibitem[Carlberg(2009)]{Carlberg09a}
  Carlberg,~R.~G. 2009, \apj, 705, L223
\bibitem[Carlberg(2012)]{Carlberg12a}
Carlberg,~R.~G. 2012, \apj, 748, 20
\bibitem[Dehnen(2000)]{Dehnen00a}
  Dehnen,~W. 2000, \apj, 536, L39
\bibitem[Dehnen(2002)]{Dehnen02a}
  Dehnen,~W. 2002, J.~Comput.~Phys., 179, 27
\bibitem[Eyre \& Binney(2011)]{Eyre11a}
  Eyre,~A. \& Binney,~J. 2011, \mnras, 413, 1852
\bibitem[Gilks \& Wild(1992)]{Gilks92a}
  Gilks,~W.~R. \& Wild,~P. 1992, Applied Statistics, 41, 337
\bibitem[Helmi \& White(1999)]{Helmi99a}
  Helmi,~A. \& White,~S.~D.~M. 1999, \mnras, 307, 495
\bibitem[Johnston \etal(1999)]{Johnston99a}
  Johnston,~K.~V., Zhao,~H., Spergel,~D.~N., \& Hernquist,~L. 1999, \apj, 512, L109
\bibitem[Koposov \etal(2010)]{Koposov10a}
  Koposov,~S.~E., Rix,~H.-W., \& Hogg,~D.~W. 2010, \apj, 712, 260
\bibitem[McGill \& Binney(1990)]{McGill90a}
  McGill,~C. \& Binney,~J. 1990, \mnras, 244, 634
\bibitem[McMillan \& Binney(2008)]{McMillan08a}
  McMillan,~P.~J. \& Binney,~J.~J. 2008, \mnras, 390, 429
\bibitem[Ngan \& Carlberg(2014)]{Ngan14a}
  Ngan,~W.~H.~W. \& Carlberg,~R.~G. 2014, \apj, submitted
\bibitem[Pe{\~n}arrubia \etal(2012)]{Penarrubia12a}
  Pe{\~n}arrubia, J., Koposov,~S.~E., \& Walker,~M.~G. 2012, \apj, 760, 2
\bibitem[Price-Whelan \& Johnston(2013)]{PriceWhelan13a}
  Price-Whelan,~A.~M. \& Johnston,~K.~V.~2013, \apj, 778, L12
\bibitem[Sanders(2012)]{Sanders12a}
  Sanders,~J. 2012, \mnras, 426, 128
\bibitem[Sanders \& Binney(2013a)]{Sanders13a}
  Sanders,~J. \& Binney,~J. 2013a, \mnras, 433, 1813
\bibitem[Sanders \& Binney(2013b)]{Sanders13b}
  Sanders,~J. \& Binney,~J. 2013b, \mnras, 433, 1826
\bibitem[Shoemake(1985)]{Shoemake85a}
  Shoemake,~K. 1985, ACM SIGGRAPH Computer Graphics 3, 45
\bibitem[Teuben(1995)]{Teuben95a}
  Teuben,~P.~J. 1995, in Astronomical Data Analysis Software and Systems IV, 
  ed.~R.~Shaw, H.~E.~Payne and J.~J.~E.~Hayes., PASP Conf Series 77, 398
\bibitem[Tremaine(1999)]{Tremaine99a}
  Tremaine,~S. 1999, \mnras, 307, 877
\bibitem[Yoon \etal(2011)]{Yoon11a}
  Yoon,~J.~H., Johnston,~K.~V., \& Hogg,~D.~W. 2011, \apj, 731, 58
\end{thebibliography}

>>>>

Tidal streams hold enormous promise as probes of both the large-scale
structure of the Milky Way (MW) halo's density distribution
\citep[\eg,][]{Johnston99a,Koposov10a} and its small-scale
fluctuations \citep{Carlberg12a}. However, two factors
have hampered the practical use of tidal streams in obtaining
constraints on the MW gravitational potential. First, streams do not
trace a single orbit, which has led to confusion over how to best fit
streams and over how problematic the single-orbit approximation really
is \citep{Eyre11a,Sanders13a}. Second, approaches that go beyond the
single-orbit assumption encounter practical difficulties of
computational cost and observational data quality making many of these
approaches impractical for real, noisy data
\citep{Sanders13b,PriceWhelan13a}. Observed gaps in tidal streams may
be due to interactions with dark--matter subhalos \citep{Yoon11a}, but
spurious underdensities could be created by the dynamics of stream
stars. This hinders our ability to use underdensities in star counts
along a tidal stream in order to constrain the number of encounters
with dark satellites and their masses \citep{Ngan14a}. Fast,
generative models of tidal streams would greatly benefit both of these
applications.

@@

\begin{figure}[t!]
 \includegraphics[width=0.8\textwidth,clip=]{gd1_pdf_l.ps}
 \caption{Density distribution as a function of Galactic
   longitude. The smooth solid line shows the fiducial model's
   prediction, while the histogram shows the density along the
   simulated stream. The simple fiducial stream model can accurately
   predict the density distribution along the
   stream.}\label{fig:gd1_pdf_l}
%python plot_pdfs_l.py ../tex/gd1_pdf_l.ps
\end{figure}

@@

Similar procedures can be followed to evaluate other projections and
marginalizations of the PDF, \eg, $p(b|l)$ for the observed track of
the stream on the sky, to convolve the PDF with observational
uncertainties, and to calculate moments of the PDF, \eg, the density
and velocity dispersion along the stream. Another example is shown in
\figurename~\ref{fig:gd1_pdf_l}. This Figure shows the model's density
as a function of Galactic longitude and compares it to that of the
simulated stream in the final snapshot (\ie, that of
\figurename~s~\ref{fig:gd1_lbd} and \ref{fig:gd1_lbv}). The model
density here is calculated using a Monte Carlo mock stream sample,
drawn as described in \sectionname~\ref{sec:mock}, rather than through
direct numerical integration.

@@

\bibitem[{{Binney} \& {Tremaine}(2008)}]{binneytremaine}
  Binney,~J. \& Tremaine,~S. 2008, Galactic Dynamics: Second Edition
\bibitem[Binney(2008)]{Binney08a}
  Binney,~J. 2008, \mnras, 386, L47
\bibitem[Binney(2012)]{Binney12a}
  Binney,~J. 2012, \mnras, 426, 1324
\bibitem[Bovy \etal(2011)]{Bovy11a}
  Bovy,~J., Hogg,~D.~W., \& Roweis,~S.~T. 2011, Ann. Appl. Stat. 5, 1657, arXiv:0905.2979v1
\bibitem[Carlberg(2012)]{Carlberg12a}
Carlberg,~R.~G. 2012, \apj, 748, 20
\bibitem[Dehnen(2000)]{Dehnen00a}
  Dehnen,~W. 2000, \apj, 536, L39
\bibitem[Dehnen(2002)]{Dehnen02a}
  Dehnen,~W. 2002, J.~Comput.~Phys., 179, 27
\bibitem[Eyre \& Binney(2011)]{Eyre11a}
  Eyre,~A. \& Binney,~J. 2011, \mnras, 413, 1852
\bibitem[Gilks \& Wild(1992)]{Gilks92a}
  Gilks,~W.~R. \& Wild,~P. 1992, Applied Statistics, 41, 337
\bibitem[Helmi \& White(1999)]{Helmi99a}
  Helmi,~A. \& White,~S.~D.~M. 1999, \mnras, 307, 495
\bibitem[Johnston \etal(1999)]{Johnston99a}
  Johnston,~K.~V., Zhao,~H., Spergel,~D.~N., \& Hernquist,~L. 1999, \apj, 512, L109
\bibitem[Koposov \etal(2010)]{Koposov10a}
  Koposov,~S.~E., Rix,~H.-W., \& Hogg,~D.~W. 2010, \apj, 712, 260
\bibitem[McGill \& Binney(1990)]{McGill90a}
  McGill,~C. \& Binney,~J. 1990, \mnras, 244, 634
\bibitem[McMillan \& Binney(2008)]{McMillan08a}
  McMillan,~P.~J. \& Binney,~J.~J. 2008, \mnras, 390, 429
\bibitem[Ngan \& Carlberg(2014)]{Ngan14a}
  Ngan,~W.~H.~W. \& Carlberg,~R.~G. 2014, \apj, submitted
\bibitem[Pe{\~n}arrubia \etal(2012)]{Penarrubia12a}
  Pe{\~n}arrubia, J., Koposov,~S.~E., \& Walker,~M.~G. 2012, \apj, 760, 2
\bibitem[Price-Whelan \& Johnston(2013)]{PriceWhelan13a}
  Price-Whelan,~A.~M. \& Johnston,~K.~V.~2013, \apj, 778, L12
\bibitem[Sanders(2012)]{Sanders12a}
  Sanders,~J. 2012, \mnras, 426, 128
\bibitem[Sanders \& Binney(2013a)]{Sanders13a}
  Sanders,~J. \& Binney,~J. 2013a, \mnras, 433, 1813
\bibitem[Sanders \& Binney(2013b)]{Sanders13b}
  Sanders,~J. \& Binney,~J. 2013b, \mnras, 433, 1826
\bibitem[Shoemake(1985)]{Shoemake85a}
  Shoemake,~K. 1985, ACM SIGGRAPH Computer Graphics 3, 45
\bibitem[Teuben(1995)]{Teuben95a}
  Teuben,~P.~J. 1995, in Astronomical Data Analysis Software and Systems IV, 
  ed.~R.~Shaw, H.~E.~Payne and J.~J.~E.~Hayes., PASP Conf Series 77, 398
\bibitem[Tremaine(1999)]{Tremaine99a}
  Tremaine,~S. 1999, \mnras, 307, 877
\bibitem[Yoon \etal(2011)]{Yoon11a}
  Yoon,~J.~H., Johnston,~K.~V., \& Hogg,~D.~W. 2011, \apj, 731, 58
\end{thebibliography}
